---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  out.width = "100%"
)
```

<!-- badges: start -->
<!-- badges: end -->

# TrumpLies

The goal of TrumpLies is to makes available in R the database of Donald Trump's false claims
    compiled by Daniel Dale at *The Toronto Star* for further analysis
    and data visualization.

## Installation

This package is presently maintained in a private repo on Github, pending public release of the 
database. If you can read this, you can install the package via

```{r install-github, eval=FALSE}
# install.packages("devtools")
devtools::install_github("friendly/TrumpLies")
```

## Example

This is a basic example showing a simple histogram of frequencies of Trump lies by month using `ggplot2`:

```{r ex1}
## basic example code
library(TrumpLies)
library(ggplot2)
library(scales)
data(TrumpLies)

ggplot(TrumpLies, aes(x=date))  +
  geom_histogram(binwidth=20, colour="black", fill="lightblue") +
  scale_x_date(labels = scales::date_format("%Y-%m"),
               breaks = seq(min(TrumpLies$date)-5, max(TrumpLies$date)+5, 30)) +
  ylab("Number of False Claims") + 
  xlab("Year and Month") +
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust = 1, hjust=1))

```

